\documentclass[10pt]{article}
%\usepackage{array, xcolor}%, lipsum}%, bibentry}
\usepackage{xcolor,array}
\usepackage{pbox}
\usepackage{booktabs}
%\usepackage[margin=3cm]{geometry}
\usepackage[left=1in,top=1in,right=1in,bottom=1in,nohead]{geometry}

\newcommand{\punt}[1]{}
\newcommand{\textbfx}[1]{{\bf #1}}
\newcommand{\textitx}[1]{{\it #1}}

\textwidth 6.65truein
\textheight 9.5truein
\oddsidemargin -0.4in
\topmargin -0.6in

\usepackage[hidelinks=true]{hyperref}
\usepackage{longtable}
\usepackage{paralist}

\title{\bfseries\huge Ajay Brahmakshatriya}
\author{ajaybr@mit.edu}
\date{}

\definecolor{lightgray}{gray}{0.8}
%\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
%\newcolumntype{L}{>{\raggedright}p{0.14\textwidth}}
%\newcolumntype{R}{p{0.8\textwidth}}
%\newcolumntype{R}{p{0.9\textwidth}}

%\newcommand \VRule{\color{lightgray}\vrule width 0.5pt}
\newcommand \VRule{}

\newcommand{\specialcell}[2][c]{%
    \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\begin{document}

%\maketitle
%\vspace{1em}
\section*{{\bfseries\LARGE Ajay Brahmakshatriya}}

\begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}



\href{mailto:ajaybr@mit.edu}{ajaybr@mit.edu} \newline 
Massachusetts Institute of Technology \newline
32 Vassar Street\newline
\#32-G788 \newline
Cambridge, MA (02139) \newline
United States 
 & 
Graduate Student \newline
COMMIT Group \newline
Computer Science and Artificial Intelligence Lab \newline
\url{https://intimeand.space} \newline
+1 617 401 5751 \\
\end{tabular}


\section*{Education}
%\begin{tabular}{L!{\VRule}R}
\begin{tabular}{l!{\VRule}l}
September'20-Present 	&{\bf Ph.D. in Computer Science, Massachusetts Institute of Technology} 					                \\
September'18-September'20 	&{\bf S.M. in Computer Science, Massachusetts Institute of Technology} 					                \\
August'12-June'16	&{\bf B.Tech in Computer Science(Honors), IIT Hyderabad} 	\\
%& Runner up to the President's Gold medal \punt{including all departments of BTech 2016}\\
\punt{
July'11-June'12	&{\bf J.H. Ambani School, Central Board for Secondary Education}				                & 94.0\% \\
July'09-June'10 	&{\bf J.H. Ambani School, Central Board for Secondary Education} 					                & 95.8\% \\
}
\end{tabular}


\section*{Interests}
Programming languages, Compilers and Systems


\section*{Work Experience}
\begin{tabular}{l!{\VRule}l}
%\begin{longtable}{l!{\VRule} p{15cm} !{\VRule}}
July'16-July'18 & {\bf Research Fellow, Microsoft Research India, Bangalore } \\
%May'15-July'15 & {\bf Intern, Software Development Engineer, Amazon India, Bangalore } \\
%\end{longtable}
\end{tabular}

\section*{Current Research Projects}
%\begin{tabular}{l!{\VRule}p{15cm}!{\VRule}}
\begin{longtable}{l!{\VRule} p{15cm} }

January'19-Present & {\bf BuildIt: A type based multi-stage programming language extension for imperative languages} \\
Advisor       & {\bf Prof. Saman Amarasinghe} \\
 & A type based multi-stage programming library for imperative languages like C++ \newline \\

May'20-Present & {\bf NetBlocks: An Extensible Compiler for Generating Ad-Hoc Network Protocols } \\
Advisor & {\bf Prof. Saman Amarasinghe and Prof. Manya Ghobadi} \\
 & Optimizing network applications and network stack implementations using compiler techniques \newline \\

%September'18-Present & {\bf A Unified Graph Framework for Achieving High-Performance across Algorithms, Graph Types,and Architectures} \\ 
%Advisor       & {\bf Prof. Saman Amarasinghe, Prof. Julian Shun} \\ 
% & Generating effecient CUDA code for graph algorithms. New GraphIR for portable code generation across multiple platforms. \newline \\ 
\end{longtable}

\punt {
\begin{tabular}{l!{\VRule}l}
Programming		&	X86/64 Assembly, C, C\texttt{++}\\
Tools			&	LLVM\\
%Tools			&	LLVM, Visual Studio, Git\\
%Scripting		&	Python, Bash, Batch\\
%Compiler-tools  &   Flex, Yacc
\multicolumn{2}{l}{Some of my projects are hosted at \url{https://github.com/AjayBrahmakshatriya} } \\
\end{tabular}
}

\section*{Awards}
\begin{itemize}
\item Federick C. Hennie III Award for Teaching Excellence \\
\item Distinguished Paper Award, International Symposium on Code Generation and Optimization (CGO), 2023 \\
\item Best Paper Award, International Symposium on Code Generation and Optimization (CGO), 2021 \\
\end{itemize}

\section*{Service}
\textbf{Artifact Evaluation Committee Member}
\begin{itemize}
\item Static Analysis Symposium (SAS), 2021 \\ 
\item Symposium on Operating Systems and Principles (SOSP), 2021 \\
\item International Symposium on Code Generation and Optimization (CGO), 2022 \\
\end{itemize}

\section*{Publications}
\textbfx{Ajay Brahmakshatriya}, Chris Rinard, Manya Ghobadi and Saman Amarasinghe. NetBlocks: Staging Layouts for High-Performance Custom Host Network Stacks 
\textitx{Proceedings of the International Symposium on Programming Language Design and Implementation (PLDI), 2024}. 
\\ \\
\textbfx{Ajay Brahmakshatriya}, and Saman Amarasinghe. D2X: An eXtensible conteXtual Debugger for Modern DSLs 
\textitx{Proceedings of the International Symposium on Code Generation and Optimization (CGO), 2023}. \textbfx{Distinguished Paper Award}.
\\ \\
\textbfx{Ajay Brahmakshatriya}, and Saman Amarasinghe. GraphIt to CUDA compiler in 2021 LOC: A case for high-performance DSL implementation via staging with BuilDSL
\textitx{Proceedings of the International Symposium on Code Generation and Optimization (CGO), 2022}.
\\ \\
%\textbfx{Ajay Brahmakshatriya}, and Saman Amarasinghe. GraphIt to CUDA compiler in 2021 LOC: A case for high-performance DSL implementation via staging with BuilDSL
Nishil Talati, Di Jin, Haojie Ye, \textbf{Ajay Brahmakshatriya}, Saman Amarasinghe, Trevor Mudge, Danai Koutra, and Ronald Dreslinski. A Deep Dive Into Understanding The Random Walk-Based Temporal Graph Learning
\textitx{Proceedings of the IEEE International Symposium on Workload Characterization (IISWC), 2021}.
\\ \\
\textbfx{Ajay Brahmakshatriya}, Emily Furst, Victor Ying, Claire Hsu, Changwan Hong, Max Ruttenberg, Yunming Zhang, Tommy Jung, Dustin Richmond, Michael Taylor, Julian Shun, Mark Oskin, Daniel Sanchez, and Saman Amarasinghe. Taming the Zoo: The Unified GraphIt Compiler Framework for Novel Architectures. To appear in \textitx{Proceedings of the IEEE/ACM International Symposium on Computer Architecture (ISCA), 2021}.
\\ \\
\textbfx{Ajay Brahmakshatriya}, and Saman Amarasinghe. BuildIt: A Type-Based Multi-stage Programming Framework for Code Generation in C++. 
\textitx{Proceedings of the International Symposium on Code Generation and Optimization (CGO), 2021}.
\\ \\
\textbfx{Ajay Brahmakshatriya}, Yunming Zhang, Changwan Hong, Shoaib Kamil, Julian Shun, and Saman Amarasinghe. Compiling Graph Applications for GPUs with GraphIt. 
\textitx{Proceedings of the International Symposium on Code Generation and Optimization (CGO), 2021}. \textbfx{Best Paper Award}. 
\\ \\
Jessica Ray, \textbfx{Ajay Brahmakshatriya}, Richard Wang, Shoaib Kamil, Albert Reuther, Vivienne Sze, and Saman Amarasinghe. Domain-Specific Language Abstractions for Compression.
\textitx{Proceedings of the Data Compression Conference (DCC), 2021}. 
\\ \\
Yunming Zhang, \textbfx{Ajay Brahmakshatriya}, Xinyi Chen, Laxman Dhulipala, Shoaib Kamil, Saman Amarasinghe, and Julian Shun. Optimizing Ordered Graph Applications with GraphIt. 
\textitx{Proceedings of the International Symposium on Code Generation and Optimization (CGO), 2020}. 
\\ \\
Yishen Chen, \textbfx{Ajay Brahmakshatriya}, Charith Mendis, Alex Renda, Eric Atkinson, Ondrej Sykora, Saman Amarasinghe, and Michael Carbin. BHive: A Benchmark Suite and Measurement Framework for Validating x86-64 Basic Block Performance Models. 
\textitx{Proceedings of the IEEE International Symposium on Workload Characterization (IISWC), 2020}.
\\ \\
\textbfx{Ajay Brahmakshatriya}, Piyus Kedia, Hamed Nemati, Derrick McKee, Deepak Garg, Akash Lal, Aseem Rastogi, Anmol Panda, and Pratik Bhatu. CONFLLVM: A Compiler for Enforcing Data Confidentiality in Low-Level Code. 
\textitx{Proceedings of the Fourteenth EuroSys Conference (EUROSYS), 2019}.
\\ \\
Prashant Sharma, \textbfx{Ajay Brahmakshatriya}, Thomas Valerrian Pasca, Bheemarjun Reddy Tamma, and Anthony Franklin. LWIR: LTE-WLAN Integration at RLC Layer with Virtual WLAN Scheduler for Efficient Aggregation. 
\textitx{Proceedings of the IEEE Global Communications Conference (GLOBECOM), 2016}.
%\section*{Skill Set}
\\ \\ 


%\section*{Academic Achievements and Experiences}
%\begin{itemize}
%\item Runner up to the President's Gold medal including all departments of BTech 2016. 
%\item Awarded the academic excellence award for 2014, 2016 during BTech. 
%%\item Teaching assistant for 3 Semester for Principles of Programming Languages and Compilers courses.
%%\item Secured 1863 Rank in IIT-JEE, 2012 out of 500,000 students who appeared for the test
%\end{itemize}
%
%
%\section*{Extra-Curriculars}
%\begin{itemize}
%\item Winner of Microsoft CTF competitions - Hackon(Winner) and Build the shield(Runner up)
%\item Creatives core for Elan 2015 and Web Coordinator for Elan 2014, the Cultural and Technical festival of IIT Hyderabad.
%\item Core member of KLUDGE and INFERO, the hacking and programming clubs of IIT Hyderabad for the year 2013-2014.
%\end{itemize}
%
%
%\section*{Hobby Projects} 
%\begin{itemize}
%\item emu-NES - An X64 JIT emulator for Nintendo Entertainment System (MOS6502 processor) with efficient PPU rendering. \punt{https://github.com/AjayBrahmakshatriya/emu-NES}
%\item {\sf Some of my projects are hosted at \url{https://github.com/AjayBrahmakshatriya} } \\*
%\end{itemize}
%\section*{Key Courses Undertaken}


%\begin{table}[h]
%\begin{tabular}{llll}
%Compilers & Advanced Compiler Optimization & Operating Systems & Advanced Operating Systems \\
%Computer Architecture & Computer Networks & Topics in Advanced Networking & Machine Learning \\
%\end{tabular}
%\end{table}

\end{document}
