\documentclass[10pt]{article}
%\usepackage{array, xcolor}%, lipsum}%, bibentry}
\usepackage{xcolor,array}
\usepackage{pbox}
\usepackage{booktabs}
%\usepackage[margin=3cm]{geometry}
\usepackage[left=1in,top=1in,right=1in,bottom=1in,nohead]{geometry}


\textwidth 6.65truein
\textheight 9.5truein
\oddsidemargin -0.4in
\topmargin -0.6in

\usepackage[hidelinks=true]{hyperref}
\usepackage{longtable}
\usepackage{paralist}

\title{\bfseries\huge Ajay Brahmakshatriya}
\author{a.ajay9470@gmail.com}
\date{}

\definecolor{lightgray}{gray}{0.8}
%\newcolumntype{L}{>{\raggedleft}p{0.14\textwidth}}
%\newcolumntype{L}{>{\raggedright}p{0.14\textwidth}}
%\newcolumntype{R}{p{0.8\textwidth}}
%\newcolumntype{R}{p{0.9\textwidth}}
\newcommand\VRule{\color{lightgray}\vrule width 0.5pt}
\newcommand{\specialcell}[2][c]{%
    \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\begin{document}

%\maketitle
%\vspace{1em}
\section*{{\bfseries\LARGE Ajay Brahmakshatriya}}

\begin{minipage}[ht]{0.60\textwidth}
\href{mailto:a.ajay9470@gmail.com}{a.ajay9470@gmail.com}\\
Microsoft Research, India \\
No.9 "Vigyan", Lavelle road\\
Bangalore, Karnataka (560001)
India

\end{minipage}
\begin{minipage}[ht]{0.48\textwidth}
Research Fellow\\
Systems and Programming Languages Group\\
Microsoft Research\\
\url{https://ajaybrahmakshatriya.github.io} \\
+91 8722 704 770\\
\end{minipage}
%\vspace{10pt}


\section*{Education}
%\begin{tabular}{L!{\VRule}R}
\begin{tabular}{l!{\VRule}ll}
August'12-June'16	&{\bf B.Tech in Computer Science(Honors), Indian Institute of Technology Hyderabad} 	& 9.74/10 \\
& Runner up to the President's Gold medal including all departments of BTech 2016\\
July'11-June'12	&{\bf J.H. Ambani School, Central Board for Secondary Education}				                & 94.0\% \\
July'09-June'10 	&{\bf J.H. Ambani School, Central Board for Secondary Education} 					                & 95.8\% \\
\end{tabular}


\section*{Interests}
Programming languages, Compiler and Systems research

\section*{Publications}
\begin{tabular}{l!{\VRule}p{15cm}}
%\begin{longtable}{l!{\VRule} p{15cm} !{\VRule}}

%PLDI'18  & {\bf An Instrumenting Compiler for Enforcing Confidentiality in Low-Level Code } \\
%(\textit{Under submission}) & \\
%\\
GLOBECOM'16 & {\bf LWIR: LTE-WLAN Integration at RLC Layer with Virtual WLAN Scheduler for Efficient Aggregation } \\
%\end{longtable}
\end{tabular}

\section*{Work Experience}
\begin{tabular}{l!{\VRule}p{15cm}}
%\begin{longtable}{l!{\VRule} p{15cm} !{\VRule}}
July'16-Present & {\bf Research Fellow, Microsoft Research India, Bangalore } \\
May'15-July'15 & {\bf Intern, Software Development Engineer, Amazon India, Bangalore } \\
%\end{longtable}
\end{tabular}

\section*{Major Projects}
%\begin{tabular}{l!{\VRule}p{15cm}!{\VRule}}
\begin{longtable}{l!{\VRule} p{15cm} }

July'16-Present & {\bf An Instrumenting Compiler for Enforcing Confidentiality in Low-Level Code } \\
Advisor       & {\bf Dr. Akash Lal, Senior Researcher, MSR India} \\
 & Memory partitioning and instrumentation techniques for preventing leak of confidential data in low level languages in presence of active attackers. \newline \\

August'15-January'16 & {\bf LWIR: LTE-WLAN Integration at RLC Layer with Virtual WLAN Scheduler for Efficient Aggregation} \\
Advisor        & {\bf Dr. Bheemarjuna Reddy Tamma, Professor, CSE department, IIT Hyderabad} \\
 & Tunneling LTE RLC frames over WiFi channel for increased throughput with a scheduling algorithm that reduced waiting time and out of order delivery \newline \\

January'16-August'16 & {\bf Efficient code generation for stencil computations on spherical domains} \\
Advisor    & {\bf Dr. Ramakrishna Upadrasta, Professor, CSE department, IIT Hyderabad} \\
 & Efficient strategies for smashing a thin spherical domain with large number of points to minimize memory utilization and execution time. Execution tiled appropriately in space and time to minimize cache misses. \newline \\

August'14-January'15 & {\bf X86 compiler for the language ‘COOL’ (a subset of Java)} \\
Advisor    & {\bf Dr. Ramakrishna Upadrasta, Professor, CSE department, IIT Hyderabad} \\
\newline \\ 
\newline \\
\newline \\
August'14-January'15 & {\bf Enhancements to Minx OS} \\
Advisor        & {\bf Dr. Bheemarjuna Reddy Tamma, Professor, CSE department, IIT Hyderabad} \\
     & Modifications to Minix operating system to implement 2 new schedulers
\newline \\ 
\end{longtable}

\section*{Skill Set}
\begin{tabular}{l!{\VRule}l}
Programming		&	X86/64 Assembly, C, C\texttt{++}\\
Tools			&	LLVM, Visual Studio, Git\\
Scripting		&	Python, Bash, Batch\\
Compiler-tools  &   Flex, Yacc
\end{tabular}
\newline {\sf Some of my projects are hosted at \url{https://github.com/AjayBrahmakshatriya} } \\*

\section*{Academic Achievements and Experiences}
\begin{compactitem}
\item Runner up to the President's Gold medal including all departments of BTech 2016. 
\item Awarded the academic excellence award for 2014, 2016 during BTech. 
\item Teaching assistant for 3 Semester for Principles of Programming Languages and Compilers courses.
\item Secured 1863 Rank in IIT-JEE, 2012 out of 500,000 students who appeared for the test
\end{compactitem}


\section*{Extra-Curriculars}
\begin{compactitem}
\item Winner of Microsoft CTF competitions - Hackon(Winner) and Build the shield(Runner up)
\item Creatives core for Elan 2015 and Web Coordinator for Elan 2014, the Cultural and Technical festival of IIT Hyderabad.
\item Core member of KLUDGE and INFERO, the hacking and programming clubs of IIT Hyderabad for the year 2013-2014.
\end{compactitem}


\section*{Hobby Projects} 
\begin{compactitem}
\item emu-NES - An X64 JIT emulator for Nintendo Entertainment System (MOS6502 processor) with efficient PPU rendering. \\ https://github.com/AjayBrahmakshatriya/emu-NES
\end{compactitem}

\section*{Key Courses Undertaken}


\begin{table}[h]
\begin{tabular}{llll}
Compilers & Advanced Compiler Optimization & Operating Systems & Advanced Operating Systems \\
Computer Architecture & Computer Networks & Topics in Advanced Networking & Machine Learning \\
\end{tabular}
\end{table}

\end{document}
